% Term paper proposal template - Ilona Sparks
% CSC 300: Professional Responsibilities
% Dr. Clark Turner

% One Column Format
\documentclass[12pt]{article}

\usepackage{setspace}
\usepackage{url}

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{letterpaper}


\begin{document}

\title{\vfill Maintenance Courses in a Software Engineering Curriculum} %\vfill gives us the black space at the top of the page
\author{
James Pearson \vspace{10pt} \\
CSC 300: Professional Responsibilities  \vspace{10pt} \\
Section 1 \vspace{10pt} \\
Dr. Clark Turner \vspace{10pt} \\
}
\date{January 23, 2012} %Or use \Today for today's Date

\maketitle

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
Although software maintenance makes up most of the work a software engineer will do in the workplace, Cal Poly requires Software Engineering undergraduates to take only two courses that cover software maintenance.  Considering this, is it ethical for the Computer Science department to state that the program is designed to produce software professionals?
\end{abstract}

\thispagestyle{empty} %remove page number from title page, but still keep it as pg #1
\newpage

%%%%%%%%%%%%%%%%%%%%
%%% Known Facts  %%%
%%%%%%%%%%%%%%%%%%%%
\section{Facts}
The Cal Poly catalog states that the Software Engineering undergraduate degree "prepares students to become software professionals who develop software 
products on time, within budget, and that meet customer requirements". \cite{catalogDept}  It also says that the program differs from the similar Computer Science undergraduate degree program in four ways, one of which is having "classes [that] include significant learning in engineering and management areas such as quality assurance, testing, metrics, maintenance, configuration management and interpersonal management skills." \cite{catalogDept}

George E. Stark claims that "maintenance consumes between 60 percent and 80 percent of a typical product's total software lifecycle expenditures". \cite{stark97}  Girish Parekh says that it is two-thirds of the lifecycle and consumes at least 50 percent of most programmers' time. \cite{parekh}

Andrews and Lutfiyya, while preparing in 1998 for a software maintenance course at the University of Western Ontario, found no courses at other universities in which students performed maintenance activities on legacy software. \cite{Andrews:2000:ERS:794188.794320} They also found that "most computer science programs offer[ed] no more than two software engineering course". \cite{Andrews:2000:ERS:794188.794320}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Research Question %%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Question}
Given that Cal Poly requires Software Engineering undergraduates to take only two courses that cover software maintenance, is it ethical for the Computer Science department to state that the program is designed to produce software professionals?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Extant Arguments from External Sources %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extant arguments}
Andrews and Lutfiyya found that their software maintenance course "gave students valuable experience in the qualitatively different task of software maintenance". \cite{Andrews:2000:ERS:794188.794320}  Engle, Ford and Korson state that it is "important for students to have experienced [software maintenance]". \cite{engle}

I have not found any arguments against including maintenance as a part of software engineering curriculum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Analytic principles %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Applicable analytic principles}
The ACM's Software Engineering Code explicitly mentions software maintenance as one of the things software engineers should focus on. \cite{secode}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Abstract your Expected Analysis %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Abstract of Expected Analysis}
Contrast the amount of time spent on software maintenance in the field with the amount of time devoted to it in education.  Then, discuss how the SE code states that software engineers should be educated in software maintenance.

% cite all the references you want in your annotated bibliography that you cite in the paper
\nocite{catalogDept}
\nocite{catalogCourses}
\nocite{stark97}
\nocite{stark99}
\nocite{Lientz:1978:CAS:359511.359522}
\nocite{parekh}
\nocite{Yau:1986:SSD:5980.5985}
\nocite{Andrews:2000:ERS:794188.794320}
\nocite{engle}
\nocite{Slimick:1997:UCS:523979.794218}
\nocite{secode}


\bibliographystyle{termpaperproposal/IEEEannot}

\bibliography{termpaperproposal/proposal}
\end{document}
