\documentclass[11pt]{article}
% Use wide margins, but not quite so wide as fullpage.sty
\marginparwidth 0.5in 
\oddsidemargin 0.25in 
\evensidemargin 0.25in 
\marginparsep 0.25in
\topmargin 0.25in 
\textwidth 6in \textheight 8 in
% That's about enough definitions

\begin{document}
\author{James Pearson}
\title{Peer Review - James Shirley}
\maketitle

\section{Paper Summary}

Megaupload was a file-hosting site that facilitated the transfer of files between users.  Anti-piracy groups claimed that Megaupload specifically facilitated illegal transfers of copy-righted material.  The primary discussion in the paper is whether the programmers employed by Megaupload were violating the SE Code by creating the service.

\section{Feedback}

A number of copy-editing suggestions were made in the margins of the physical draft; due to the suitability for this type of comment in that form (and difficulty in displaying them useful in this form), they will not generally be duplicated in this document.

\subsection{Facts}

I'm not convinced that software used to be consumed, and I don't see anything in the cited Techdirt article to support that.  No information provided about the current events (arrest of founder, shutdown of domain).  Other than that, a good number of relevant facts, organized well (but needing more paragraph breaks).

\subsection{Research Question}

As I wrote on the paper, the question appears to be questioning whether sites should allow user-generated content at all; the analysis aims more at facilitating piracy, rather than merely providing a way for it to happen.

\subsection{Importance}

A good mention of the different groups the question affects, but there should be some discussion of why we should care about those groups.

\subsection{Harm Argument}

As mentioned on the physical copy, the organization of this section is a bit muddled - ethical systems shouldn't be introduced until we need them (we've concluded that piracy harms content authors; why is this harm bad?).  Expand a bit by including the sources you've cited earlier.

\subsection{Infinite Good Argument}

Same thing as previous regarding organization.

\subsection{Why the SE Code Applies}

Good reasoning.  More citations, as explained in margin notes, would strengthen the argument.

\subsection{Retention of Illegal Media}

Some rather extensive margin notes on this section; the definition alone was not convincing to me.

\subsection{Morality of Actions}

As mentioned in the notes, I don't see how the renumeration of the programmers working on Megaupload is relevant - if it is, please expand.  Also, I'm not convinced that ``fair and just renumeration'' should apply to Megaupload's users or content authors.

\subsection{Awareness of Actions}

Good.

\end{document}
